---
title: "Homework 1"
author: "Jiawei Ye"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
```


This is the first homework of P8105.

## Problem 1

The following code chunk creates the data frame as required. 
```{r create_uniform_distribution}
set.seed(100)
dataframe = tibble(
  sample = runif(10, min = 0, max = 5),
  morethan2 = c(sample[1:10] > 2),
  p1_cha = c('a','b','c','d','e','f','g','h','i','j'),
  p1_fac = factor(c(length = 10))
)

dataframe$p1_cha
dataframe$p1_fac
length(dataframe$p1_fac)
```

The following code chunk tries to convert logical/character/factor vectors to numerical vector.
```{r convert, eval = FALSE}
as.numeric(dataframe$morethan2)
as.numeric(dataframe$p1_cha)
as.numeric(dataframe$p1_fac)
```

## Problem 2

The following code chunk creates the data frame as required.
```{r create_normal_distribution}
norm_distri = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  x_plus_y_more_than0 = c(x[1:1000] + y[1:1000] > 0 ),
  num_vec = as.numeric(x_plus_y_more_than0),
  fac_vec = as.factor(x_plus_y_more_than0)
)
```

The size of the dataset is 

The following code chunk creates the scatter plot of `x_plus_y_more_than0` in `norm_distri`
```{r scatter_plot_logical}
ggplot(norm_distri, aes(x = x, y = y, color = x_plus_y_more_than0)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

The following code chunk creates the scatter plot of `num_vec` in `norm_distri`
```{r scatter_plot_numerical}
ggplot(norm_distri, aes(x = x, y = y, color = num_vec)) + geom_point()
```

The following code chunk creates the scatter plot of `fac_vec` in `norm_distri`
```{r scatter_plot_factor}
ggplot(norm_distri, aes(x = x, y = y, color = fac_vec)) + geom_point()
```